Integration of national demographic-disturbance relationships into local caribou population viability projections can reduce uncertainty and inform monitoring decisions

### 2024-08-27 analysis/paper/paper.Rmd
add author contributions, number sections

>>>>

# Author contributions
**Josie Hughes:** Conceptualization, Formal analysis, Methodology, Investigation,
Supervision, Software, Writing – original draft, Writing – review and editing, 
Visualization
**Sarah Endicott:** Resources, Software, Writing – review and editing
**Anna M Calvert:** Conceptualization, Writing – original draft, Writing – review and editing
**Cheryl A Johnson:** Conceptualization, Writing – review and editing
